Pillar 1 - Sequential Pattern Mining

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
updates SR_TPF

SR_TPF are manually computed
```{r}
# current, past, not_yet
SR_TPF <- d_transcript_cum                         %>%
  select(sequenceID, eventID, course_current, course_not_so_far)    %>%
  unnest(course_current, .drop = F)                %>%
  unnest(course_not_so_far)                        %>%
  left_join(
    select(d_transactions, 
           sequenceID, eventID, item, PF), 
    by= c("sequenceID" = "sequenceID", "eventID" = "eventID", "item" = "course_so_far")
    )                                              %>%
  select(sequenceID,eventID, course_not_so_far, course_current, PF) %>%
  rename(
    lhs="course_not_so_far", 
    rhs.x = "course_current", 
    rhs.PF = "PF")                                 %>%
  mutate(num_transactions = n())                   %>%
  group_by(lhs)                                    %>%
  mutate(
    num_lhs = n(),
    support_lhs         = num_lhs / num_transactions
    )                                              %>%
  group_by(rhs.x)                                  %>%
  mutate(
    num_rhs.x           = n(),
    support_rhs.x       = num_rhs.x / num_transactions
         )                                         %>%
  group_by(rhs.x,rhs.PF)                           %>%
  mutate(
    num_rhs.PF          = n(),
    support_rhs.PF      = num_rhs.PF / num_transactions
  )                                                %>%
  group_by(lhs, rhs.x)                             %>%
  mutate(
    num_rule_x          = n(),
    support_rule_rhs.x  = num_rule_x / num_transactions
  )                                                %>%
  group_by(lhs, rhs.x, rhs.PF)                     %>%
  mutate(
    num_rule_PF          = n(),
    support_rule_rhs.PF  = num_rule_PF / num_transactions,
    support_rhs_bounded  = num_rule_PF / num_rule_x
         )                                         %>%
  ungroup()                                        %>%
  mutate(
    confidence                   = support_rule_rhs.PF / support_lhs,
    confidence_bounded           = support_rhs_bounded / support_lhs, #not sure about this 
    lift                         = confidence / support_rhs.PF,
    lift_bounded                 = confidence_bounded /support_rhs_bounded #not sure about this
  )
```

We save and remove objects:
```{r saving and rm SR}
#Saving sequence rules
save(
    SR_taken, SR_PF, SR_HL, SR_G,
    #SR_TPF,
    #SR_expanded_Grade,
    file = "App/SR.RDATA")

>>>>

SR_TPF are manually computed
```{r}
# current, past, not_yet
SR_TPF <- d_transcript_cum                         %>%
  select(sequenceID, eventID, course_current, course_not_so_far)    %>%
  unnest(course_current, .drop = F)                %>%
  unnest(course_not_so_far)                        %>%
  left_join(
    select(d_transactions$TPF, 
           sequenceID, eventID, item, PF), 
    by= c("sequenceID" = "sequenceID", "eventID" = "eventID", "course_current" = "item")
    )                                              %>%
  select(sequenceID,eventID, course_not_so_far, course_current, PF) %>%
  rename(
    lhs="course_not_so_far", 
    rhs.x = "course_current", 
    rhs.PF = "PF")                                 %>%
  mutate(num_transactions = n())                   %>%
  group_by(lhs)                                    %>%
  mutate(
    num_lhs = n(),
    support_lhs         = num_lhs / num_transactions
    )                                              %>%
  group_by(rhs.x)                                  %>%
  mutate(
    num_rhs.x           = n(),
    support_rhs.x       = num_rhs.x / num_transactions
         )                                         %>%
  group_by(rhs.x,rhs.PF)                           %>%
  mutate(
    num_rhs.PF          = n(),
    support_rhs.PF      = num_rhs.PF / num_transactions
  )                                                %>%
  group_by(lhs, rhs.x)                             %>%
  mutate(
    num_rule_x          = n(),
    support_rule_rhs.x  = num_rule_x / num_transactions
  )                                                %>%
  group_by(lhs, rhs.x, rhs.PF)                     %>%
  mutate(
    num_rule_PF          = n(),
    support_rule_rhs.PF  = num_rule_PF / num_transactions,
    support_rhs_bounded  = num_rule_PF / num_rule_x
         )                                         %>%
  ungroup()                                        %>%
  mutate(
    confidence                   = support_rule_rhs.PF / support_lhs,
    confidence_bounded           = support_rhs_bounded / support_lhs, #not sure about this 
    lift                         = confidence / support_rhs.PF,
    lift_bounded                 = confidence_bounded /support_rhs_bounded #not sure about this
  )
```

We save and remove objects:
```{r saving and rm SR}
#Saving sequence rules
save(
    SR_taken, SR_PF, SR_HL, SR_G,
    SR_TPF,
    #SR_expanded_Grade,
    file = "App/SR.RDATA")
